Kids LRTI tracking

### 2020-07-28 lrti_tracking.Rmd
update LRTI tracking

---
title: "Kids LRTI tracking"
author: "Ethan Walker"
date: "Started 6 April 2020, Updated 9 April 2020"
output: pdf_document 
---

@@

```{r}
# LRTI Diagnosis data
lrti_diagnosis_data <- health_data_merged %>% 
  # select relevant health data
  select(area, home, home_winter_id, winter_id, child_id_num, 
         visit_date, csq_date:sibling_school, treatment_assigned) %>% 
  filter(!is.na(visit_date)) %>% 
  full_join(child_home_winter, by = c("area", "home_winter_id", "child_id_num")) %>% 
  filter(home_winter_id == 19)
  # This is the most broad way of distinguishing if a child was sick
  # Careful when filtering here. Could still make cases that these vars didn't catch
  # Best to have a look through all rows, then use this to filter data down so it
  # is easier to work with to assess dates/at-risk times
  filter(csq_sick_2_weeks == "Yes" | csq_still_sick == "Yes") %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  ungroup()

>>>>

---
title: "Kids LRTI tracking"
author: "Ethan Walker"
date: "Started 6 April 2020, Updated 28 July 2020"
output: pdf_document 
---

@@

```{r}
# LRTI Diagnosis data
lrti_diagnosis_data <- health_data_merged %>% 
  # select relevant health data
  select(area, home, home_winter_id, winter_id, child_id_num, 
         visit_date, csq_date:sibling_school, treatment_assigned) %>% 
  filter(!is.na(visit_date)) %>% 
  full_join(child_home_winter, by = c("area", "home_winter_id", "child_id_num")) %>%

# 6 homes have LRTI data, but actually dropped. Notes on those homes below:
# AK HWID 19/Child ID 25: No record that they participated except initial med visits/CSQs. Likely dropped.
# AK HWID 83/Child ID 70: Dropped prior to winter 1
# NN HWID 32/Child ID 45: No record that they participated except initial med visits/CSQs. Likely dropped.
# NN HWID 162/Child ID 171: Dropped prior to winter 1
# NN HWID 164/Child ID 173: Dropped prior to winter 1
# NN HWID 213/Child ID 197: Dropped prior to winter 1
# I confirmed that all of the above homes dropped, so filtering them from dataset

  filter(!is.na(home)) %>% 
  filter(!is.na(paul_lrti)) %>%

# This filtered data contains all observations for kids with LRTI diagnosis of "Yes" or "Debating"
# Next steps will be to:
  # Select necessary variables to identify dates and other info for analysis
  # Identify where they left off assigning dates previously
  # Look through LRTI "No" designations and make sure Paul didn't miss any potential diagnoses
  # Assign inital dates for those that don't have them
    # Make notes along the way for a meeting with Paul to confirm final dates

  select(area, child_id_num, home_winter_id, paul_lrti, paul_comments) %>% 
  arrange(area, child_id_num)
